### 2015-02-16 paper/exprs.tex
using a layout and expression evaluation

\subsection*{Using a Layout}

\subsection*{Expression Evaluation}

>>>>

\subsection*{Using a Layout}
The runtime analogue of using a L-value is using a layout.
Affine values are replaced by void and copyable values are left untouched.
It is not defined for $\void$, which prevents expression evalutation from utilizing
uninitialized memory. A program that tries to do so will get stuck.
\newline

\fbox{$\textsc{use} : \textrm{Layout} \to \textrm{Layout}$}

\[
\begin{array}{lcl}
\textsc{use}(z) &=& z \\
\textsc{use}(\own{\ga}) &=& \void \\
\textsc{use}(\refval{\qimm}{\ga}) &=& \refval{\qimm}{\ga} \\
\textsc{use}(\refval{\qmut}{\ga}) &=& \void
\end{array}
\]

Note that $\textsc{use}(l) = l'$ implies $\textsc{droppable}(l')$.
Once we use a value, we know we can safely deallocate it.

\subsection*{Expression Evaluation}
Evaluating expressions is straightforward.
The only unusual aspect is the case of using the value at a L-value.
To prevent copies of affine values, we must overwrite the only value
with the used version. If it is a copyable value, then it will remain unchanged.
If it is an affine value, then it will be replaced with $\void$.
Note that this means the heap resulting from expression evaluation is either
unchanged or a more deinitialized version of the starting heap.
Also note that the result heap may temporarily contain an orphan when considered alone,
but not when considered together with the result layout.
\newline

\fbox{$\ev{V;H}{e}{l;H'}$}

\begin{mathpar}
  \infer[EE-INT]{ }{\ev{V;H}{z}{z;H}} \and
  \infer[EE-REF]
    {\ev{V;H}{\lv{x}{p}}{\ga}}
    {\ev{V;H}{\tyref{\lt}{q}{\lv{x}{p}}}{\refval{q}{\ga};H}} \and
  \infer[EE-USE]
    {\ev{V;H}{\lv{x}{p}}{\ga} \\
     \Read{H}{\ga}{l} \\
     \textsc{write}(H,\ga,\textsc{use}(l),H')
    }
    {\ev{V;H}{\lv{x}{p}}{l;H'}}
\end{mathpar}
